% ============================================================
%  HW02 - Domain Testing on EShop
%  FR-01 Account Registration -- Domain Testing & Boundary Value Analysis
%  Standalone report; compile with pdflatex (T5 + babel for Vietnamese strings).
% ============================================================
\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc}
\usepackage{lmodern}
\usepackage[vietnamese,english]{babel}
\usepackage[margin=2cm]{geometry}
\usepackage{longtable}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[table,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcommand{\ec}[1]{\textbf{#1}}

\title{HW02 Domain Testing --- FR-01 Account Registration\\[2pt]
\large Domain Testing \& Boundary Value Analysis}
\author{Group Software-Testing-G02}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Feature under test}
\textbf{FR-01 --- Account registration} (Pool A). Registration is implemented in two
layers:
\begin{itemize}[leftmargin=*]
  \item \textbf{UI layer:} \texttt{frontend-web/src/pages/Register.jsx} --- a form with
  \emph{name}, \emph{email}, \emph{password}. It performs the \emph{only} validation in the
  whole feature: a client-side ``strong password'' regular expression. On success it
  \texttt{POST}s to the API and navigates to \texttt{/login}.
  \item \textbf{API layer:} \texttt{POST /api/register} (\texttt{backend/server.js}) ---
  inserts \verb|{name, email, password}| straight into the \texttt{users} table with
  \emph{no} validation, \emph{no} uniqueness check and the password stored in plain text.
\end{itemize}

\noindent\textbf{Stated password rule} (UI help text, \texttt{Register.jsx}):
\begin{quote}
``T\'ối thiểu 8 k\'ý tự, c\'ó chữ hoa, chữ thường, số v\`a k\'ý tự đặc biệt.''
(\emph{At least 8 characters, with uppercase, lowercase, a digit and a \textbf{special
character}.})
\end{quote}

\noindent\textbf{Actually enforced client regex} (\texttt{Register.jsx}, line 15):
\begin{verbatim}
/^(?=.*[a-z])(?=.*[A-Z])(?=.*\d)(?=.*\s)[A-Za-z\d\s]{8,}$/
\end{verbatim}
This regex requires a \textbf{whitespace} character (\verb|(?=.*\s)|) and, because the
character class is \verb|[A-Za-z\d\s]|, \textbf{forbids every special character}. It is the
exact opposite of the stated rule and is the central defect this report targets.

\paragraph{Legend for the test tables.}
Because execution is performed by the student against a running EShop, each case carries an
\textbf{Expected (per spec)} value --- what a correct implementation should do --- and a
\textbf{Predicted (source analysis)} value --- what the current code will do, derived by
reading the source (\emph{not} an executed result). The \textbf{Actual / Pass--Fail} column
is intentionally left blank in the source; it is filled after running the tests. Any case
whose Predicted value diverges from Expected is a candidate bug.

% ------------------------------------------------------------
\section{Step 1 --- Identify variables}
\label{sec:vars}
Every input and output of the registration feature, including implicit variables (field
length, password character classes, uniqueness, persisted representation).

\begin{center}
\begin{tabular}{L{2.6cm} L{2.3cm} L{1.7cm} L{7.8cm}}
\toprule
\textbf{Variable} & \textbf{Type} & \textbf{I/O} & \textbf{Notes} \\
\midrule
name       & string (TEXT)  & Input  & UI: HTML \texttt{required}. No length/format rule. Backend: none. \\
email      & string (TEXT)  & Input  & UI: \texttt{required}, but \texttt{type="text"} $\Rightarrow$ no format check. Backend: none; column \emph{not} \texttt{UNIQUE}. \\
password   & string (TEXT)  & Input  & Only validated by the client regex above. Backend: none; stored in plain text. \\
password length     & integer (derived) & Input & Ordered variable; boundary at 8 (regex \verb|{8,}|). \\
has\_lower / has\_upper / has\_digit & boolean (derived) & Input & Character-class conditions of the regex. \\
has\_whitespace     & boolean (derived) & Input & Regex \emph{requires} it (defect). \\
has\_special\_char  & boolean (derived) & Input & Regex \emph{forbids} it (defect); spec requires it. \\
email uniqueness    & boolean (derived) & Input & Whether the email already exists; never checked. \\
\midrule
HTTP status         & integer & Output & \texttt{200} on insert, \texttt{500} only on a DB error (none reachable). \\
response body       & JSON    & Output & \verb|{message, id}| or \verb|{error}|. \\
client error msg    & string  & Output & ``Mật khẩu qu\'á yếu\ldots'' when regex fails. \\
persisted row       & DB row  & Output & \texttt{id, name, email, password(plaintext), role='user'}. \\
navigation          & route   & Output & Redirect to \texttt{/login} on success. \\
\bottomrule
\end{tabular}
\end{center}

% ------------------------------------------------------------
\section{Step 2 --- Characterise each variable's domain}
\label{sec:domains}
For each input, the \emph{valid} domain per the intended specification and the constraint
\emph{actually} enforced by the code.

\begin{center}
\begin{tabular}{L{2.3cm} L{6.2cm} L{6.4cm}}
\toprule
\textbf{Variable} & \textbf{Valid domain (intended spec)} & \textbf{Constraint actually enforced} \\
\midrule
name     & Non-empty, human name; reasonable length (e.g. 1--100 chars). & UI blocks empty (\texttt{required}); whitespace-only passes. API accepts anything incl.\ \texttt{NULL}. No max length. \\
email    & Non-empty, valid email syntax (\texttt{local@domain.tld}), unique across users. & UI blocks empty only. No syntax check anywhere. No uniqueness check (column not \texttt{UNIQUE}). Leading/trailing spaces not trimmed. \\
password & $\ge 8$ chars \emph{and} contains lowercase, uppercase, digit \emph{and} a special character. & Client regex: $\ge 8$ chars \emph{and} lowercase \emph{and} uppercase \emph{and} digit \emph{and} \textbf{whitespace}, using only \verb|[A-Za-z\d\s]| (\textbf{special chars rejected}). API: no rule at all. \\
\bottomrule
\end{tabular}
\end{center}

\noindent The mismatch between columns 2 and 3 for \emph{password} (whitespace required
instead of special char; specials forbidden) and for \emph{email} (no syntax/uniqueness)
is the raw material for the partitions in Step~3.

% ------------------------------------------------------------
\section{Step 3 --- Equivalence partitioning (Domain Testing)}
\label{sec:ec}
Each input domain is split into valid and invalid equivalence classes. Format classes
(empty, whitespace-only, wrong syntax, special characters, injection-like, very long,
duplicate) are included, per the technique.

\begin{center}
\begin{longtable}{L{1.4cm} L{1.6cm} L{1.9cm} L{5.4cm} L{3.4cm}}
\toprule
\textbf{Class} & \textbf{Variable} & \textbf{Valid/Invalid} & \textbf{Description / rationale} & \textbf{Representative value} \\
\midrule
\endhead
\ec{EC-N1} & name & Valid   & Normal non-empty name & \texttt{Nguyen Van A} \\
\ec{EC-N2} & name & Invalid & Empty (missing required field) & \verb|""| \\
\ec{EC-N3} & name & Invalid & Whitespace-only (looks filled, semantically empty) & \verb|"   "| \\
\ec{EC-N4} & name & Valid*  & Very long name (no documented max) & 100{,}000 chars \\
\ec{EC-N5} & name & Valid*  & Unicode / diacritics & \texttt{Nguyễn Đặng} \\
\midrule
\ec{EC-E1} & email & Valid   & Well-formed, not yet used & \texttt{new.user@domain.com} \\
\ec{EC-E2} & email & Invalid & Malformed syntax & \texttt{notanemail} \\
\ec{EC-E3} & email & Invalid & Empty (missing required field) & \verb|""| \\
\ec{EC-E4} & email & Invalid & Duplicate of an existing account & \texttt{test@eshop.com} \\
\ec{EC-E5} & email & Invalid & Same address with surrounding spaces & \verb|" test@eshop.com "| \\
\ec{EC-E6} & email & Invalid & Injection-like payload & \texttt{x'; DROP TABLE users;--} \\
\midrule
\ec{EC-P1} & password & Regex-valid* & Passes the client regex: has ws, no special, $\ge 8$ & \texttt{Passw0rd 1} \\
\ec{EC-P2} & password & Spec-valid & Genuinely strong: upper+lower+digit+special, no ws & \texttt{Password123!} \\
\ec{EC-P3} & password & Invalid & Missing lowercase & \texttt{PASSW0RD 1} \\
\ec{EC-P4} & password & Invalid & Missing uppercase & \texttt{passw0rd 1} \\
\ec{EC-P5} & password & Invalid & Missing digit & \texttt{Password x} \\
\ec{EC-P6} & password & Invalid & Missing whitespace (defect condition) & \texttt{Password1} \\
\ec{EC-P7} & password & Invalid & Contains a special character & \texttt{Passw0rd !} \\
\ec{EC-P8} & password & Invalid & Length $<8$ & \texttt{Aa1 bcd} \\
\ec{EC-P9} & password & Invalid & Empty & \verb|""| \\
\bottomrule
\end{longtable}
\end{center}

\noindent\textbf{Notation.} ``Regex-valid*'' means \emph{accepted by the current client
regex} even though it violates the stated rule (no special char). ``Spec-valid'' means it
satisfies the \emph{documented} rule but is \emph{rejected} by the code. ``Valid*'' marks
inputs a correct system should accept but which no layer constrains. These starred classes
are exactly where the feature is expected to be wrong.

% ------------------------------------------------------------
\section{Step 4 --- Identify boundaries}
\label{sec:bounds}
Registration has one genuinely \emph{ordered}, numerically bounded variable and several
implicit ones:

\begin{itemize}[leftmargin=*]
  \item \textbf{Password length} --- boundary at \textbf{8}, \emph{inclusive} on the valid
  side (regex \verb|{8,}|). This is the only well-defined numeric boundary and the target of
  the BVA in Step~6. The character-class conditions (lower/upper/digit/whitespace/special)
  are boolean partitions, not ordered boundaries, so they are covered by Step~3, not BVA.
  \item \textbf{Name / email length} --- lower boundary is ``non-empty'' (1 char) enforced
  only by the UI \texttt{required} attribute; \emph{no} upper boundary is documented or
  enforced (SQLite \texttt{TEXT} is unbounded). The upper edge is therefore an
  \emph{undefined} boundary --- itself a finding (Step~8).
  \item \textbf{Email uniqueness} --- a degenerate ``count'' boundary: 0 existing copies
  (valid) vs $\ge 1$ existing copies (should be invalid). Never enforced.
\end{itemize}

\noindent\textbf{Key observation.} The length boundary (\verb|{8,}|) is implemented
\emph{correctly} --- there is no off-by-one at 8. The planted defects live in the
\emph{character-class} conditions (whitespace-required, special-forbidden), which is why
Domain partitioning (Step~3) finds more bugs here than pure BVA. A naive ``just do BVA on
length'' pass would miss them.

\section{Step 5 --- Domain matrix (on-point / off-point)}
\label{sec:matrix}
Classic $1\times1$ analysis of the password-length boundary. Every value below is
constructed to satisfy all \emph{other} regex conditions (one lowercase, one uppercase, one
digit, one space, only allowed characters) so that length is the single variable under test.

\begin{center}
\begin{tabular}{L{3.4cm} L{2.6cm} L{2.4cm} L{2.9cm} L{2.9cm}}
\toprule
\textbf{Boundary} & \textbf{on-point (=8)} & \textbf{off-point (7)} & \textbf{Expected on} & \textbf{Expected off} \\
\midrule
password length $\ge 8$ & \texttt{Aa1 bcde} (8) & \texttt{Aa1 bcd} (7) & Accept (regex passes) & Reject (too short) \\
\bottomrule
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{L{3.4cm} L{4.0cm} L{4.0cm}}
\toprule
 & \textbf{in-point (interior valid)} & \textbf{out-point (clearly outside)} \\
\midrule
password length $\ge 8$ & \texttt{Aa1 bcdefgh} (11) $\to$ Accept & \verb|""| (length 0) $\to$ Reject \\
\bottomrule
\end{tabular}
\end{center}

\noindent The ``pass'' side is length~$\ge 8$. Predicted behaviour matches Expected for this
boundary (length is correct); the divergences appear only when the class conditions are
varied (Step~7).

% APPEND-BELOW
\end{document}
